Abb Analysis

### 2017-02-07 abbDataAnalysis_Script.Rmd
glob.updates

  str.data$pot.occ.rate <- str.data$bookings / (366 - (366 * str.data$block.rate))

@@

  imp.rents <- imputeRents(ltr.df=ltr.data, 
                           str.df=str.data, 
                           mod.spec=ltr.mod.spec,
                           clip.field='suburb')

  str.glob <- merge(str.data, imp.rents$str, by='property.id')

@@

HERE HERE HERE

@@

  impx.revs <- revenueEngine(str.df=ltr.imp, 
                             ltr.df=str.imp,
                             rate.field='imp.rate',
                             rent.field='imp.rent',
                             occ.field='imp.occ',
                             dom.field='imp.dom')

  str.imp$ltr.imp.revenue <- impx.revs$ltr
  ltr.imp$str.imp.revenue <- impx.revs$str

@@

  comp.revs <- compareRevenues(str.imp)

  str.imp <- merge(str.imp, comp.revs, by='property.id')

@@

  mrkt.table <- createCompTable(str.imp, 'sub.mrkt')

@@

  sm.col <- abb.col[c(1, 3, 6, 5, 2)]

  twotwo.bar.plot <- 
    ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    facet_grid(~rev.type) +
    scale_fill_manual(values=sm.col) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none')

@@

  rawocc.pplot <- makePrefPlot(str.imp,
                               x.field='pot.occ.rate',
                               y.field='str.ext.pref',
                               group.field='host.type',
                               smooth=TRUE,
                               smooth.span=.75)
  rawocc.pplot <- rawocc.pplot +
    xlab('\nOccupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  str.revs$sub.mrkt <- factor(str.imp$sub.mrkt, 
                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
  ggplot(str.imp, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
    geom_density(alpha=.3) +
    facet_wrap(~sub.mrkt) +
    scale_color_manual(values=sm.col) +
    scale_fill_manual(values=sm.col) +
    scale_x_continuous(breaks=seq(0, 1, by=.5),
                       labels=c('0%', '50%', '100%')) +
    ylab('') +
    xlab('Occupancy Rate') +
    theme(legend.position='none',
          axis.line=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.y=element_blank())

@@

  str.imp$occ.qtl <- makeWtdQtl(str.imp$occ.rate, 
                                      return.type='rank') 
  str.imp$rate.qtl <- makeWtdQtl(str.imp$med.rate, 
                                  return.type='rank')

@@

  qtlocc.pplot <- makePrefPlot(str.imp,
                               x.field='occ.qtl',
                               y.field='str.act.pref',
                               group.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  qtlocc.pplot <- qtlocc.pplot +
    xlab('\nQualtile of Occupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  rate.hm <- makeHeatMap(str.imp,
                x.field='occ.rate',
                y.field='nightly.rate',
                color.field='str.act',
                bins=c(.05, 25),
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))

@@

  rate.hm.svm <- makeHeatMap(str.revs,
                         x.field='occ.rate',
                         y.field='nightly.rate',
                         color.field='str.act',
                         bins=c(.05, 25),
                         svm=T, 
                         alpha.count=F,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

@@

  qtl.hm <- makeHeatMap(str.revs,
                         x.field='occ.qtl',
                         y.field='rate.qtl',
                         color.field='str.act',
                         bins=c(5, 5),
                         svm=F, 
                         alpha.count=T,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

@@

  qtl.hm.svm <- makeHeatMap(str.revs,
                        x.field='occ.qtl',
                        y.field='rate.qtl',
                        color.field='str.act',
                        bins=c(5, 5),
                        svm=T, 
                        alpha.count=F,
                        add.points=T,
                        fill.colors=c(abb.col[1], abb.col[5]))

@@

  svm.rate <- makeSVM(str.revs,
                     x.field='occ.rate',
                     y.field='nightly.rate',
                     z.field='str.act',
                     svm.type='C-svc',
                     svm.kernel='polydot',
                     poly.degree=4,
                     expand.factor=100)

  svm.qtl <- makeSVM(str.revs,
                      x.field='occ.qtl',
                      y.field='rate.qtl',
                      z.field='str.act',
                      svm.type='C-svc',
                      svm.kernel='polydot',
                      poly.degree=4,
                      expand.factor=100)

  market.ratio <- data.frame(type=c('rate', 'qtl'),
                             actual=rep(mean(str.revs$str.act), 2),
                             fitted=c(mean(svm.rate$orig$fitted),
                                      mean(svm.qtl$orig$fitted)),
                             svm=c(mean(svm.rate$pred$pred),
                                   mean(svm.qtl$pred$pred)))
```

>>>>

  str.data$pot.occ.rate <- (str.data$bookings * str.data$extr.par) / (366 - (366 * str.data$block.rate))

@@

  imp.data <- imputeLtrRents(ltr.df=ltr.data, 
                               str.df=str.data, 
                               mod.specs=ltr.mod.spec,
                               match.factor='suburb')

From the imputed results, we extract the base data (with imputed values) as well as the model summaries.

  # Extract out DFs (only those that imputed)
  str.glob <- merge(str.data, imp.data$imp.rent, by='property.id')

@@

@@

  str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7)

@@

  comp.revs <- compareRevenues(str.glob)

  str.glob <- merge(str.glob, comp.revs, by='property.id')

abbImputeCompare <- function(str.df,
                             ltr.df,
                             mod.spec, 
                             match.factor=NULL,
                             split.field=NULL){

  if(!is.null(split.field)){

    str.list <- split(str.df, str.df[ ,split.field])
    ltr.list <- split(ltr.df, ltr.df[ ,split.field])

    str.list <- list(str.df)
    ltr.list <- list(ltr.df)

  imp.list <- list()

  for(il in 1:length(str.list)){

    imp.temp <- imputeLtrRents(ltr.df=ltr.df, 
                                     str.df=str.df, 
                                     mod.specs=mod.spec,
                                     match.factor=match.factor)

    str.list[[il]] <- merge(str.list[[il]], imp.temp$imp.rent, by='property.id')
    imp.list[[il]] <- imp.temp

    str.list[[il]]$imp.dom <- imputeDOM(str.list[[il]], 
                                        ltr.data[[il]], 
                                        calc.type='median')
    str.list[[il]]$ltr.imp.revenue <- str.list[[il]]$imp.rent * (52 - str.list[[il]]$imp.dom / 7)

    comp.revs <- compareRevenues(str.list[[il]])

    str.list[[il]] <- merge(str.list[[il]], 
                            comp.revs, 
                            by='property.id')

  str.df <- rbind.fill(str.list)
  str.df$split.field <- split.field

@@

  mrkt.table <- createCompTable(str.glob, 'sub.mrkt')

@@

  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
  ht.col <- abb.col(c(2, 4, 10, 9)]

  bar.plot <- 
    ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    facet_grid(~rev.type) +
    scale_fill_manual(values=sm.col) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none')

@@

  rawocc.pplot <- makePrefPlot(str.glob,
                               x.field='pot.occ.rate',
                               y.field='str.pot.pref',
                               group.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  rawocc.pplot <- rawocc.pplot +
    xlab('\nOccupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  str.glob$sub.mrkt <- factor(str.glob$sub.mrkt, 
                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
  ggplot(str.glob, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
    geom_density(alpha=.3) +
    facet_wrap(~sub.mrkt) +
    scale_color_manual(values=sm.col) +
    scale_fill_manual(values=sm.col) +
    scale_x_continuous(breaks=seq(0, 1, by=.5),
                       labels=c('0%', '50%', '100%')) +
    ylab('') +
    xlab('Occupancy Rate') +
    theme(legend.position='none',
          axis.line=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.y=element_blank())

@@

  str.glob$occ.qtl <- makeWtdQtl(str.glob$occ.rate, 
                                      return.type='rank') 
  str.glob$rate.qtl <- makeWtdQtl(str.glob$med.rate, 
                                  return.type='rank')

@@

  qtlocc.pplot <- makePrefPlot(str.glob,
                               x.field='occ.qtl',
                               y.field='str.act.pref',
                               group.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  qtlocc.pplot <- qtlocc.pplot +
    xlab('\nQualtile of Occupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  rate.hm <- makeHeatMap(str.glob,
                x.field='occ.rate',
                y.field='nightly.rate',
                color.field='str.act.pref',
                bins=c(.05, 25),
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))

@@

  rate.hm.svm <- makeHeatMap(str.glob,
                         x.field='occ.rate',
                         y.field='nightly.rate',
                         color.field='str.act.pref',
                         bins=c(.05, 25),
                         svm=T, 
                         alpha.count=F,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

@@

  qtl.hm <- makeHeatMap(str.glob,
                         x.field='occ.qtl',
                         y.field='rate.qtl',
                         color.field='str.act.pref',
                         bins=c(5, 5),
                         svm=F, 
                         alpha.count=T,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

@@

  qtl.hm.svm <- makeHeatMap(str.glob,
                        x.field='occ.qtl',
                        y.field='rate.qtl',
                        color.field='str.act.pref',
                        bins=c(5, 5),
                        svm=T, 
                        alpha.count=F,
                        add.points=T,
                        fill.colors=c(abb.col[1], abb.col[5]))

@@

  svm.rate <- makeSVM(str.glob,
                     x.field='occ.rate',
                     y.field='nightly.rate',
                     z.field='str.act.pref',
                     svm.type='C-svc',
                     svm.kernel='polydot',
                     poly.degree=4,
                     expand.factor=100)

  svm.qtl <- makeSVM(str.glob,
                      x.field='occ.qtl',
                      y.field='rate.qtl',
                      z.field='str.act.pref',
                      svm.type='C-svc',
                      svm.kernel='polydot',
                      poly.degree=4,
                      expand.factor=100)

  market.ratio <- data.frame(type=c('rate', 'qtl'),
                             actual=rep(mean(str.glob$str.act.pref), 2),
                             fitted=c(mean(svm.rate$orig$fitted),
                                      mean(svm.qtl$orig$fitted)),
                             svm=c(mean(svm.rate$pred$pred),
                                   mean(svm.qtl$pred$pred)))
```
